---
title: "SNA Reachiability 17_ACESSO I) O tempo gasto para acessar este serviço impede a realização ativades em conjunto. (var15)"
author: "Leonardo Martins"
date: "17 de julho de 2016"
output: 
  html_document: 
    fig_caption: yes
    fig_height: 12
    fig_width: 12
    keep_md: yes
    number_sections: yes
    theme: flatly
    toc: yes
---
SNA Descritive Analysis from "Projeto Redes de Atenção às pessoas que consomem álcool e outras Drogas em Juiz de Fora-MG   Brazil"  - SNArRDJF

Here you can find a basic script to analysis data from SNArRDJF - this script was elaborated considering its use for orther matrix adjacency data from SNArRDJF - Here we are going to analyse:

# 17_ACESSO I) O tempo gasto para acessar este serviço impede a realização ativades em conjunto. (var15)

`#########################
`# Basic Preparation #####
`#########################

#Loading objects generated with previous script 
```{r, echo=TRUE, fig.height=12, fig.width=12, message=FALSE, warning=FALSE}
rm(list = ls()) # removing previous objects to be sure that we don't have objects conflicts name
load("~/SNArRDJF/Robject/12_cliques_var15.RData")
```
##Reload packages
```{r, message=TRUE, warning=TRUE}
suppressMessages(library(RColorBrewer))
suppressMessages(library(car))
suppressMessages(library(xtable))
suppressMessages(library(igraph))
suppressMessages(library(miniCRAN))
suppressMessages(library(magrittr))
suppressMessages(library(keyplayer))
suppressMessages(library(dplyr))
suppressMessages(library(feather))
suppressMessages(library(visNetwork))
suppressMessages(library(knitr))
suppressMessages(library(DT))
```
##Adding phantom tools
```{r, message=TRUE, warning=TRUE}
#In order to get dinamic javascript object install those ones. If you get problems installing go to Stackoverflow.com and type your error to discover what to do. In some cases the libraries need to be intalled in outside R libs.
#devtools::install_github("wch/webshot")
#webshot::install_phantomjs()
```
##Setting a random seed - this is a good strategy to keep the same graph pattern layout in a new report generation
```{r, message=TRUE, warning=TRUE}
set.seed(123)
```

##Simplify Graph - removing loops and duble edges 
```{r, echo=T, message=FALSE, warning=FALSE}
var15<-simplify(var15) #Simplify
```


#Reachability

An actor is "reachable" by another if there exists any set of connections by which we can trace from the source to the target actor, regardless of how many others fall between them. If the data are asymmetric or directed, it is possible that actor A can reach actor B, but that actor B cannot reach actor A. With symmetric or undirected data, of course, each pair of actors either are or are not reachable to one another. If some actors in a network cannot reach others, there is the potential of a division of the network. Or, it may indicate that the population we are studying is really composed of more than one sub-populations.

#Declaring Reachability function calculation for each vertex
```{r, echo=TRUE, fig.height=12, fig.width=12, message=FALSE, warning=FALSE}
reachability <- function(g, m) {
  reach_mat = matrix(nrow = vcount(g), ncol = vcount(g))
  for (i in 1:vcount(g)) {
    reach_mat[i,] = 0
    this_node_reach <- subcomponent(g, i, mode = m) # used "i" instead of "(i - 1)"
    
    for (j in 1:(length(this_node_reach))){
      alter = this_node_reach[j]# removed "+ 1"
      reach_mat[i, alter] = 1
      }
    }
  return(reach_mat)
  }
``` 
#Reachability - IN
```{r, echo=TRUE, fig.height=12, fig.width=12, message=FALSE, warning=FALSE}
#Reach function
var15_reach_in <- reachability(var15, 'in')

#Mean Reachbility by Vertex
var15_reach_in_vec <- vector()
for (i in 1:vcount(var15)) {
    var15_reach_in_vec[i] <- mean(var15_reach_in[i,])
}

#Adding to igraph object
V(var15)$reach_in<-var15_reach_in_vec
```
#Descriptive - Reachability - IN
```{r, echo=TRUE, fig.height=12, fig.width=12, message=FALSE, warning=FALSE}
V(var15)$reach_in <-mean(var15_reach_in[which(var15_reach_in != Inf)])
sd(var15_reach_in[which(var15_reach_in != Inf)])
```

#Reachability - OUT
```{r, echo=TRUE, fig.height=12, fig.width=12, message=FALSE, warning=FALSE}
#Reach function
var15_reach_out <- reachability(var15, 'out')

#Mean Reachbility by Vertex
var15_reach_out_vec <- vector()
for (i in 1:vcount(var15)) {
    var15_reach_out_vec[i] <- mean(var15_reach_out[i,])
}

#Adding to igraph object
V(var15)$reach_out<-var15_reach_out_vec
```

##Descriptive - Reachability  - OUT
```{r, echo=TRUE, fig.height=12, fig.width=12, message=FALSE, warning=FALSE}
mean(var15_reach_out[which(var15_reach_out != Inf)])
sd(var15_reach_out[which(var15_reach_out != Inf)])
```

#Reachbility Measures Dinamic Table
```{r, echo=T, fig.height=12, fig.width=12, message=FALSE, warning=FALSE}

#Creating a datagrame of measures
var15_reachability_df <- data.frame(var15_reach_in_vec,var15_reach_out_vec) %>% round(3)

#Adding type
var15_reachability_df <-cbind(var15_reachability_df, V(var15)$LABEL_COR)

#Adding names
names(var15_reachability_df) <- c("Reach IN", "Reach OUT","Type")

#Ordering Variables
var15_reachability_df<-var15_reachability_df[c("Type", "Reach IN", "Reach OUT")]
```
## General tabel - DT 
```{r, echo=T, fig.height=12, fig.width=12, message=FALSE, warning=FALSE}
datatable(var15_reachability_df, filter = 'top')
```

##Aggregating data from previous table - mean
```{r, echo=T, fig.height=12, fig.width=12, message=FALSE, warning=FALSE}
aggdata_mean <-aggregate(var15_reachability_df, by=list(var15_reachability_df$Type), FUN=mean, na.rm=TRUE)

names(aggdata_mean) <- c("Group","Type","Reach IN(M)", "Reach OUT(M)")
  
#Removing Type variable
aggdata_mean<-aggdata_mean[,-c(2)]
```
##Aggregating data from previous table - sd
```{r, echo=T, fig.height=12, fig.width=12, message=FALSE, warning=FALSE}
aggdata_sd <-aggregate(var15_reachability_df, by=list(var15_reachability_df$Type), FUN=sd, na.rm=TRUE) 

names(aggdata_sd) <- c("Group","Type","Reach IN(SD)", "Reach OUT(SD)")

#Removing Type variable
aggdata_sd<-aggdata_sd[,-c(2)]
```
##Merging mean and standart deviation
```{r, echo=T, fig.height=12, fig.width=12, message=FALSE, warning=FALSE}
total <- merge(aggdata_mean,aggdata_sd,by="Group")

#Rounding
Group<-total[,c(1)] #Keeping group
total<-total[,-c(1)] %>% round(3) #Rouding
total<-cbind(Group,total) #Binding toghter

#Organizing Variabels
total<-total[c("Group","Reach IN(M)","Reach IN(SD)","Reach OUT(M)","Reach OUT(SD)")]
```
##Final table with round - Transitivity
```{r, echo=T, fig.height=12, fig.width=12, message=FALSE, warning=FALSE}
datatable(total, filter = 'top')
```
#Saving objects with new variables and changes
```{r, echo=T, fig.height=12, fig.width=12, message=FALSE, warning=FALSE}
save.image("~/SNArRDJF/Robject/13_reach_var15.RData") 
```

