---
title: "SNA Betwenness Vertex 21_CONFIANÇA D) Confia em compartilhar informações internas com este serviço. (var19) "
author: "Leonardo Martins"
date: "17 de julho de 2016"
output: 
  html_document: 
    fig_caption: yes
    fig_height: 12
    fig_width: 12
    keep_md: yes
    number_sections: yes
    theme: flatly
    toc: yes
---
SNA Descritive Analysis from "Projeto Redes de Atenção às pessoas que consomem álcool e outras Drogas em Juiz de Fora-MG   Brazil"  - SNArRDJF

Here you can find a basic script to analysis data from SNArRDJF - this script was elaborated considering its use for orther matrix adjacency data from SNArRDJF - Here we are going to analyse:

# 21_CONFIANÇA D) Confia em compartilhar informações internas com este serviço. (var19) 

`#########################
`# Basic Preparation #####
`#########################

#Loading objects generated with previous script 
```{r, echo=TRUE, fig.height=12, fig.width=12, message=FALSE, warning=FALSE}
rm(list = ls()) # removing previous objects to be sure that we don't have objects conflicts name
load("~/SNArRDJF/Robject/var19_data.RData")
```
##Reload packages
```{r, message=TRUE, warning=TRUE}
suppressMessages(library(RColorBrewer))
#suppressMessages(library(car))
#suppressMessages(library(xtable))
suppressMessages(library(igraph))
#suppressMessages(library(miniCRAN))
#suppressMessages(library(magrittr))
#suppressMessages(library(keyplayer))
suppressMessages(library(dplyr))
#suppressMessages(library(feather))
#suppressMessages(library(visNetwork))
#suppressMessages(library(knitr))
suppressMessages(library(DT))
```
##Adding phantom tools
```{r, message=TRUE, warning=TRUE}
#In order to get dinamic javascript object install those ones. If you get problems installing go to Stackoverflow.com and type your error to discover what to do. In some cases the libraries need to be intalled in outside R libs.
#devtools::install_github("wch/webshot")
#webshot::install_phantomjs()
```
##Setting a random seed - this is a good strategy to keep the same graph pattern layout in a new report generation
```{r, message=TRUE, warning=TRUE}
set.seed(123)
```

##Simplify Graph - removing loops and duble edges 
```{r, echo=T, message=FALSE, warning=FALSE}
#var19<-simplify(var19) #Simplify
```

#Betweenness - Number of shortest paths going through the actor σst(i)

High betweenness centrality - vertex lies on many shortest paths. Probability that a communication from s
to t will go through i - considering σst(i).

Betweenness measures the number of shortest paths between nodes in the network that go through the node in question. Nodes with relatively high betweenness are likely to be key conduits of information flow across a network, and their removal may have a large impact on spreading phenomena.

##Betweenness Centrality -(Vertex)

Betweenness centrality based on a broker position connecting others or Number of geodesics that pass through the node or the edge. A higher number means an more important node.

#Adding weight equal one for all analysis 
```{r}
E(var19)$equalone<-1
```

###Saving objects
```{r, echo=TRUE, fig.height=12, fig.width=12, message=FALSE, warning=FALSE}
V(var19)$betweenness <- betweenness(var19, weights = E(var19)$equalone) %>% round(1)
var19_betweenness <- betweenness(var19, weights = E(var19)$equalone) %>% round(1)
```
###Betweenness Centrality - all
```{r, echo=TRUE, fig.height=12, fig.width=12, message=FALSE, warning=FALSE}
summary(var19_betweenness)
sd(var19_betweenness)
```

##Betweenness Centrality Weighted - (Vertex)
```{r, echo=TRUE, fig.height=12, fig.width=12, message=FALSE, warning=FALSE}
V(var19)$var19_betweenness_w <- betweenness(var19, weights=E(var19)$var19) %>% round(1)
var19_betweenness_w <- betweenness(var19, weights=E(var19)$var19) %>% round(1)
```
### Descriptive Betweenness Centrality Weighted - (Vertex) - all
```{r, echo=TRUE, fig.height=12, fig.width=12, message=FALSE, warning=FALSE}
summary(var19_betweenness_w)
sd(var19_betweenness_w)
```
##Centralization Betweenness
```{r, echo=TRUE, fig.height=12, fig.width=12, message=FALSE, warning=FALSE}
V(var19)$var19_centr_betweenness <- centralization.betweenness(var19)$res
var19_centr_betweenness <- centralization.betweenness(var19)
```
###Centralization
```{r, echo=TRUE, fig.height=12, fig.width=12, message=FALSE, warning=FALSE}
var19_centr_betweenness$centralization
```
###Theoretical Max
```{r, echo=TRUE, fig.height=12, fig.width=12, message=FALSE, warning=FALSE}
var19_centr_betweenness$theoretical_max
```
#Betweenness Vertex Centrality Dinamic Table
```{r, echo=TRUE, fig.height=12, fig.width=12, message=FALSE, warning=FALSE}
#Betweenness Vertex Centrality Measures Dinamic Table
#Getting  Measures
var19_betweenness <- betweenness(var19, weights=E(var19)$equalone) %>% round(1)
var19_betweenness_w <- betweenness(var19, weights=E(var19)$var19) %>% round(1)
var19_centr_betweenness <- centralization.betweenness(var19)$res %>% round(1)

#Creating a dataframe of measures
var19_df_betweenness <- data.frame(var19_betweenness,
var19_betweenness_w,
var19_centr_betweenness) %>% round(1)

#Adding type
var19_df_betweenness <-cbind(var19_df_betweenness, V(var19)$LABEL_COR)

#Adding names
names(var19_df_betweenness) <- c("Betweenness", "Betweenness Weighted", "Centralization Betweenness","Type")

#Ordering Variables
var19_df_betweenness<-var19_df_betweenness[c("Type","Betweenness", "Betweenness Weighted", "Centralization Betweenness")]
```
## General tabel for Betweenness
```{r, echo=TRUE, fig.height=12, fig.width=12, message=FALSE, warning=FALSE}
datatable(var19_df_betweenness, filter = 'top')
```
##Aggregating data from previous table - mean
```{r, echo=TRUE, fig.height=12, fig.width=12, message=FALSE, warning=FALSE}
aggdata_mean <-aggregate(var19_df_betweenness, by=list(var19_df_betweenness$Type), FUN=mean, na.rm=TRUE)

names(aggdata_mean) <- c("Group","Type","Betweenness(M)", "Betweenness Weighted(M)", "Centralization Betweenness(M)")
  
#Removing Type variable
aggdata_mean<-aggdata_mean[,-c(2)]
```
##Aggregating data from previous table - sd
```{r, echo=TRUE, fig.height=12, fig.width=12, message=FALSE, warning=FALSE}
aggdata_sd <-aggregate(var19_df_betweenness, by=list(var19_df_betweenness$Type), FUN=sd, na.rm=TRUE) 

names(aggdata_sd) <- c("Group","Type","Betweenness(SD)", "Betweenness Weighted(SD)", "Centralization Betweenness(SD)")

#Removing Type variable
aggdata_sd<-aggdata_sd[,-c(2)]
```
##Merging mean and standart deviation
```{r, echo=TRUE, fig.height=12, fig.width=12, message=FALSE, warning=FALSE}
total_table<- merge(aggdata_mean,aggdata_sd,by="Group")

#Rounding
Group<-total_table[,c(1)] #Keeping group
total_table<-total_table[,-c(1)] %>% round(1) #Rouding
total_table<-cbind(Group,total_table) #Binding toghter

#Organizing Variabels
total_table<-total_table[c("Group","Betweenness(M)","Betweenness(SD)","Betweenness Weighted(M)", "Betweenness Weighted(SD)", "Centralization Betweenness(M)","Centralization Betweenness(SD)")]
```
##Plotting final table with round
```{r, echo=TRUE, fig.height=12, fig.width=12, message=FALSE, warning=FALSE}
datatable(total_table, filter = 'top')
```

#Betweenness Vertex Centrality Dinamic Table (Natureza Governamental)
```{r, echo=TRUE, fig.height=12, fig.width=12, message=FALSE, warning=FALSE}
#Betweenness Vertex Centrality Measures Dinamic Table
#Getting  Measures
var19_betweenness <- betweenness(var19, weights=E(var19)$equalone) %>% round(1)
var19_betweenness_w <- betweenness(var19, weights=E(var19)$var19) %>% round(1)
var19_centr_betweenness <- centralization.betweenness(var19)$res %>% round(1)

#Creating a dataframe of measures
var19_df_betweenness <- data.frame(var19_betweenness,
var19_betweenness_w,
var19_centr_betweenness) %>% round(1)

#Adding type
var19_df_betweenness <-cbind(var19_df_betweenness, V(var19)$TIPO1)

#Adding names
names(var19_df_betweenness) <- c("Betweenness", "Betweenness Weighted", "Centralization Betweenness","Type")

#Ordering Variables
var19_df_betweenness<-var19_df_betweenness[c("Type","Betweenness", "Betweenness Weighted", "Centralization Betweenness")]
```
## General tabel for Betweenness
```{r, echo=TRUE, fig.height=12, fig.width=12, message=FALSE, warning=FALSE}
datatable(var19_df_betweenness, filter = 'top')
```
##Aggregating data from previous table - mean
```{r, echo=TRUE, fig.height=12, fig.width=12, message=FALSE, warning=FALSE}
aggdata_mean <-aggregate(var19_df_betweenness, by=list(var19_df_betweenness$Type), FUN=mean, na.rm=TRUE)

names(aggdata_mean) <- c("Group","Type","Betweenness(M)", "Betweenness Weighted(M)", "Centralization Betweenness(M)")
  
#Removing Type variable
aggdata_mean<-aggdata_mean[,-c(2)]
```
##Aggregating data from previous table - sd
```{r, echo=TRUE, fig.height=12, fig.width=12, message=FALSE, warning=FALSE}
aggdata_sd <-aggregate(var19_df_betweenness, by=list(var19_df_betweenness$Type), FUN=sd, na.rm=TRUE) 

names(aggdata_sd) <- c("Group","Type","Betweenness(SD)", "Betweenness Weighted(SD)", "Centralization Betweenness(SD)")

#Removing Type variable
aggdata_sd<-aggdata_sd[,-c(2)]
```
##Merging mean and standart deviation
```{r, echo=TRUE, fig.height=12, fig.width=12, message=FALSE, warning=FALSE}
total_table<- merge(aggdata_mean,aggdata_sd,by="Group")

#Rounding
Group<-total_table[,c(1)] #Keeping group
total_table<-total_table[,-c(1)] %>% round(1) #Rouding
total_table<-cbind(Group,total_table) #Binding toghter

#Organizing Variabels
total_table<-total_table[c("Group","Betweenness(M)","Betweenness(SD)","Betweenness Weighted(M)", "Betweenness Weighted(SD)", "Centralization Betweenness(M)","Centralization Betweenness(SD)")]
```
##Plotting final table with round
```{r, echo=TRUE, fig.height=12, fig.width=12, message=FALSE, warning=FALSE}
datatable(total_table, filter = 'top')
```

#Betweenness Vertex Centrality Dinamic Table (Setores)
```{r, echo=TRUE, fig.height=12, fig.width=12, message=FALSE, warning=FALSE}
#Betweenness Vertex Centrality Measures Dinamic Table
#Getting  Measures
var19_betweenness <- betweenness(var19, weights=E(var19)$equalone) %>% round(1)
var19_betweenness_w <- betweenness(var19, weights=E(var19)$var19) %>% round(1)
var19_centr_betweenness <- centralization.betweenness(var19)$res %>% round(1)

#Creating a dataframe of measures
var19_df_betweenness <- data.frame(var19_betweenness,
var19_betweenness_w,
var19_centr_betweenness) %>% round(1)

#Adding type
var19_df_betweenness <-cbind(var19_df_betweenness, V(var19)$TIPO2)

#Adding names
names(var19_df_betweenness) <- c("Betweenness", "Betweenness Weighted", "Centralization Betweenness","Type")

#Ordering Variables
var19_df_betweenness<-var19_df_betweenness[c("Type","Betweenness", "Betweenness Weighted", "Centralization Betweenness")]
```
## General tabel for Betweenness
```{r, echo=TRUE, fig.height=12, fig.width=12, message=FALSE, warning=FALSE}
datatable(var19_df_betweenness, filter = 'top')
```
##Aggregating data from previous table - mean
```{r, echo=TRUE, fig.height=12, fig.width=12, message=FALSE, warning=FALSE}
aggdata_mean <-aggregate(var19_df_betweenness, by=list(var19_df_betweenness$Type), FUN=mean, na.rm=TRUE)

names(aggdata_mean) <- c("Group","Type","Betweenness(M)", "Betweenness Weighted(M)", "Centralization Betweenness(M)")
  
#Removing Type variable
aggdata_mean<-aggdata_mean[,-c(2)]
```
##Aggregating data from previous table - sd
```{r, echo=TRUE, fig.height=12, fig.width=12, message=FALSE, warning=FALSE}
aggdata_sd <-aggregate(var19_df_betweenness, by=list(var19_df_betweenness$Type), FUN=sd, na.rm=TRUE) 

names(aggdata_sd) <- c("Group","Type","Betweenness(SD)", "Betweenness Weighted(SD)", "Centralization Betweenness(SD)")

#Removing Type variable
aggdata_sd<-aggdata_sd[,-c(2)]
```
##Merging mean and standart deviation
```{r, echo=TRUE, fig.height=12, fig.width=12, message=FALSE, warning=FALSE}
total_table<- merge(aggdata_mean,aggdata_sd,by="Group")

#Rounding
Group<-total_table[,c(1)] #Keeping group
total_table<-total_table[,-c(1)] %>% round(1) #Rouding
total_table<-cbind(Group,total_table) #Binding toghter

#Organizing Variabels
total_table<-total_table[c("Group","Betweenness(M)","Betweenness(SD)","Betweenness Weighted(M)", "Betweenness Weighted(SD)", "Centralization Betweenness(M)","Centralization Betweenness(SD)")]
```
##Plotting final table with round
```{r, echo=TRUE, fig.height=12, fig.width=12, message=FALSE, warning=FALSE}
datatable(total_table, filter = 'top')
```



##Plotting Betweenness Centrality - (Vertex)
```{r}
set.seed(123)
#Plotting based only on degree measures 
edge.start <- ends(var19, es=E(var19), names=F)[,1]

# Fixing ego
minC <- rep(-Inf, vcount(var19))
maxC <- rep(Inf, vcount(var19))
minC[1] <- maxC[1] <- 0
co <- layout_with_fr(var19, niter=10^4, minx=minC, maxx=maxC,miny=minC, maxy=maxC, weights = E(var19)$weight)

#Plotting
plot(var19, 
     layout=co,
     edge.color=V(var19)$color[edge.start],
     edge.arrow.size=(betweenness(var19, weights = E(var19)$var19)+1)/100000,
     edge.width=E(var19)$weight/10*mean(E(var19)$weight),
     edge.curved = TRUE,
     vertex.color=V(var19)$color,
     vertex.size=betweenness(var19, weights = E(var19)$var19 )/250,
     vertex.frame.color="black",
     vertex.label.color="black",
     vertex.label=get.vertex.attribute(var19,"LABEL_COR"),
     vertex.label.cex=(betweenness(var19, weights = E(var19)$var19)+1)/10000,
     vertex.label.dist=0,
     rescale=F,
     xlim=range(co[,1]), 
     ylim=range(co[,2])
     )
axis(1)
axis(2)

#Solving Problems with legend rendering 
a<-V(var19)$LABEL_COR
b<-V(var19)$color
c<-table(a,b)
d<-as.data.frame(c)
e<-subset(d, d$Freq>0)
e<-e[order(e$a,decreasing=T),] 
f<-t(e$a)
g<-t(e$b)

#Adding Legend
legend(x=range(co[,1])[2], 
       y=range(co[,2])[2],
       legend=as.character(f),
       pch=21,
       col = "#777777", 
       pt.bg=as.character(g),
       pt.cex=2,
       bty="n", 
       ncol=1,
       lty=1,
       cex = .3)

#Adding Title
    title("Network Vertex Betweenness Sized - 21_CONFIANÇA D) Confia em compartilhar informações internas com este serviço. (var19) ", sub = "Source: from authors ")
  text( 
    x=range(co[,1])[1],
    y=range(co[,2])[1], 
      labels =    sprintf("Median Betweenness: %.2f\nSD Betweenness: %.2f",
     median(betweenness(var19, weights = E(var19)$var19)), 
     sd(betweenness(var19, weights = E(var19)$var19))
             )
       )
```


##Network Plotting Based On Centralization Betweenness
```{r, echo=T, fig.height=12, fig.width=12, message=FALSE, warning=FALSE}
#Get Variable
V(var19)$var19_centr_betweenness<-(centralization.betweenness(var19)$res)/100
V(var19)$var19_color_degree<-round(V(var19)$var19_centr_betweenness,1)

#Creating brewer pallette
vertex_var19_color_degree<-
  colorRampPalette(brewer.pal(length(unique(
          V(var19)$var19_color_degree)), "Spectral"))(
            length(unique(V(var19)$var19_color_degree)))

#Saving as Vertex properties 
V(var19)$vertex_var19_color_degree<-
  vertex_var19_color_degree[as.numeric(
  cut(V(var19)$var19_color_degree,
      breaks=length(unique(V(var19)$var19_color_degree))))]

set.seed(123)
#Plotting based only on degree measures 
edge.start <- ends(var19, es=E(var19), names=F)[,1]

# Fixing ego
minC <- rep(-Inf, vcount(var19))
maxC <- rep(Inf, vcount(var19))
minC[1] <- maxC[1] <- 0
co <- layout_with_fr(var19, niter=10^4, minx=minC, maxx=maxC,miny=minC, maxy=maxC, weights = E(var19)$weight)


#PLotting
plot(var19, 
     layout=co,
     edge.color=V(var19)$vertex_var19_color_degree[edge.start],
     edge.arrow.size=closeness(var19, weights = E(var19)$var19, mode="out"),
     edge.width=E(var19)$weight/10*mean(E(var19)$weight),
     edge.curved = TRUE,
     vertex.color=V(var19)$vertex_var19_color_degree,
     vertex.size=(centralization.betweenness(var19)$res+1)/250,
     vertex.frame.color="white",
     vertex.label.color="black",
     vertex.label=get.vertex.attribute(var19,"LABEL_COR"),
     vertex.label.cex=(centralization.betweenness(var19)$res + 1)/10000,
     vertex.label.dist=0,
     rescale=F,
     xlim=range(co[,1]), 
     ylim=range(co[,2])
     )
axis(1)
axis(2)

#Solving Problems with legend rendering 
a<-V(var19)$var19_color_degree
b<-V(var19)$vertex_var19_color_degree
c<-table(a,b)
d<-as.data.frame(c)
e<-subset(d, d$Freq>0)
e<-e[order(e$a,decreasing=T),] 
f<-t(e$a)
g<-t(e$b)

#Adding Legend
legend(x=range(co[,1])[2], 
       y=range(co[,2])[2],
       legend=as.character(f),
       pch=21,
       col = "#777777", 
       pt.bg=as.character(g),
       pt.cex=2,
       bty="n", 
       ncol=1,
       lty=1,
       cex = .3)

  #Adding Title
  title("Network Centralization Betweenness - 21_CONFIANÇA D) Confia em compartilhar informações internas com este serviço. (var19) ", sub = "Source: from authors ")
  text( 
    x=range(co[,1])[1],
    y=range(co[,2])[1], 
      labels = sprintf("Median Betweenness:%.0f\nSDBetweenness: %.0f",
     median(betweenness(var19, weights = E(var19)$var19)), 
     sd(betweenness(var19, weights = E(var19)$var19))
             )
       )
```

#Saving objects with new variables and changes
```{r, echo=T, fig.height=12, fig.width=12, message=FALSE, warning=FALSE}
save.image("~/SNArRDJF/Robject/var19_data.RData")
```

