---
title: "SNA Bonacich's 4_REFERENCIA DE RECEBIMENTO CONTRAREFERENCIA (var2)"
author: "Leonardo Martins"
date: "17 de julho de 2016"
output: 
  html_document: 
    fig_caption: yes
    fig_height: 12
    fig_width: 12
    keep_md: yes
    number_sections: yes
    theme: flatly
    toc: yes
---
SNA Descritive Analysis from "Projeto Redes de Atenção às pessoas que consomem álcool e outras Drogas em Juiz de Fora-MG   Brazil"  - SNArRDJF

Here you can find a basic script to analysis data from SNArRDJF - this script was elaborated considering its use for orther matrix adjacency data from SNArRDJF - Here we are going to analyse:

# 4_REFERENCIA DE RECEBIMENTO CONTRAREFERENCIA (var2)

`#########################
`# Basic Preparation #####
`#########################

#Loading objects generated with previous script 
```{r, echo=TRUE, fig.height=12, fig.width=12, message=FALSE, warning=FALSE}
rm(list = ls()) # removing previous objects to be sure that we don't have objects conflicts name
load("~/SNArRDJF/Robject/5_betwenness_vertex_var2.RData")
```
##Reload packages
```{r, message=TRUE, warning=TRUE}
suppressMessages(library(RColorBrewer))
suppressMessages(library(car))
suppressMessages(library(xtable))
suppressMessages(library(igraph))
suppressMessages(library(miniCRAN))
suppressMessages(library(magrittr))
suppressMessages(library(keyplayer))
suppressMessages(library(dplyr))
suppressMessages(library(feather))
suppressMessages(library(visNetwork))
suppressMessages(library(knitr))
suppressMessages(library(DT))
```
##Adding phantom tools
```{r, message=TRUE, warning=TRUE}
#In order to get dinamic javascript object install those ones. If you get problems installing go to Stackoverflow.com and type your error to discover what to do. In some cases the libraries need to be intalled in outside R libs.
#devtools::install_github("wch/webshot")
#webshot::install_phantomjs()
```
##Setting a random seed - this is a good strategy to keep the same graph pattern layout in a new report generation
```{r, message=TRUE, warning=TRUE}
set.seed(123)
```

##Simplify Graph - removing loops and duble edges 
```{r, echo=T, message=FALSE, warning=FALSE}
#var2<-simplify(var2) #Simplify
```

#Bonacich's Power Centrality Scores of Network Positions

Each node's centrality score depends both on how many connections it has and how many connections its connections have.

It doesn't only matter how many friends you have. It matters how many friends your friends have.”<http://www.leonidzhukov.net/hse/2014/socialnetworks/papers/Bonacich-Centrality.pdf>

Phillip Bonacich proposed a modification of the degree centrality approach that has been widely accepted as superior to the original measure. Bonacich's idea, like most good ones, is pretty simple. The original degree centrality approach argues that actors who have more connections are more likely to be powerful because they can directly affect more other actors. This makes sense, but having the same degree does not necessarily make actors equally important.

Suppose that Bill and Fred each have five close friends. Bill's friends, however, happen to be pretty isolated folks, and don't have many other friends, save Bill. In contrast, Fred's friends each also have lots of friends, who have lots of friends, and so on. Who is more central? We would probably agree that Fred is, because the people he is connected to are better connected than Bill's people. Bonacich argued that one's centrality is a function of how many connections one has, and how many the connections the actors in the neighborhood had.

While we have argued that more central actors are more likely to be more powerful actors, Bonacich questioned this idea. Compare Bill and Fred again. Fred is clearly more central, but is he more powerful? One argument would be that one is likely to be more influential if one is connected to central others -- because one can quickly reach a lot of other actors with one's message. But if the actors that you are connected to are, themselves, well connected, they are not highly dependent on you -- they have many contacts, just as you do. If, on the other hand, the people to whom you are connected are not, themselves, well connected, then they are dependent on you. Bonacich argued that being connected to connected others makes an actor central, but not powerful. Somewhat ironically, being connected to others that are not well connected makes one powerful, because these other actors are dependent on you -- whereas well connected actors are not.

Bonacich proposed that both centrality and power were a function of the connections of the actors in one's neighborhood. The more connections the actors in your neighborhood have, the more central you are. The fewer the connections the actors in your neighborhood, the more powerful you are. There would seem to be a problem with building an algorithms to capture these ideas. Suppose A and B are connected. Actor A's power and centrality are functions of her own connections, and also the connections of actor B. Similarly, actor B's power and centrality depend on actor A's. So, each actor's power and centrality depends on each other actor's power simultaneously.

There is a way out of this chicken-and-egg type of problem. Bonacich showed that, for symmetric systems, an iterative estimation approach to solving this simultaneous equations problem would eventually converge to a single answer. One begins by giving each actor an estimated centrality equal to their own degree, plus a weighted function of the degrees of the actors to whom they were connected. Then, we do this again, using the first estimates (i.e. we again give each actor an estimated centrality equal to their own first score plus the first scores of those to whom they are connected). As we do this numerous times, the relative sizes (not the absolute sizes) of all actors scores will come to be the same. The scores can then be re-expressed by scaling by constants.


#Power (beta) Centrality Stats - (positive attenuation factor). 

##Are you more powerful if you're connected to powerful people?

```{r, results="asis"}
#Saving power as an object
var2_power_centrality_stats <- power_centrality(var2, nodes = V(var2), loops = FALSE, exponent = 0.5, rescale = FALSE, tol = 1e-07, sparse = TRUE)

#Saving power as an igraph attributte
V(var2)$var2_power_centrality_stats <-power_centrality(var2, nodes = V(var2), loops = FALSE, exponent = 0.5, rescale = FALSE, tol = 1e-07, sparse = TRUE) 

#Descriptive 
summary(var2_power_centrality_stats)
sd(var2_power_centrality_stats)
```

##Power (beta) Centrality Stats - (positive attenuation factor). 
```{r, results="asis"}
d=as.data.frame(cbind(V(var2)$LABEL_COR,round(var2_power_centrality_stats,2)))
names(d)<-c("Type", "Power(beta)")
datatable(d, filter ="top")
```

###Plotting Power Centrality Degree - (positive attenuation factor). 
```{r, echo=FALSE, fig.height=12, fig.width=12, message=FALSE, warning=FALSE}

V(var2)$var2_power_centrality_stats <-try(power_centrality(var2, nodes = V(var2), loops = FALSE, exponent = 0.5, rescale = FALSE, tol = 1e-07, sparse = TRUE))

#Setting color for each vertex based on Power
V(var2)$var2_power_centrality_stats_r<-round(V(var2)$var2_power_centrality_stats,0)

# Creating brewer pallette
vertex_col_spower <- colorRampPalette(brewer.pal(length(unique(V(var2)$var2_power_centrality_stats_r)), "Blues"))(length(unique(V(var2)$var2_power_centrality_stats_r))) 

#Saving as Vertex properties                             
V(var2)$color_spower <- vertex_col_spower[factor(V(var2)$var2_power_centrality_stats_r)]  

#Set Seed
set.seed(123)

#Plotting based only on degree measures 
edge.start <- ends(var2, es=E(var2), names=F)[,1]

# Fixing ego
minC <- rep(-Inf, vcount(var2))
maxC <- rep(Inf, vcount(var2))
minC[1] <- maxC[1] <- 0
co <- layout_with_fr(var2, niter=10000, minx=minC, maxx=maxC,miny=minC, maxy=maxC, weights = E(var2)$weight)

#PLotting
plot(var2, 
     layout=co,
     edge.color=V(var2)$color_spower[edge.start],
     edge.arrow.size=sqrt((V(var2)$var2_power_centrality_stats_r+0.001)^2)/10,
     edge.width=E(var2)$weight/(10*mean(E(var2)$weight)),
     edge.curved = TRUE,
     vertex.color=V(var2)$color_spower, 
     vertex.size=sqrt(((V(var2)$var2_power_centrality_stats_r+0.001)^2))*15,
     vertex.frame.color="#ffffff",
     vertex.label.color="black",
     vertex.label=V(var2)$V5_LABEL_LABEL,
     vertex.label.cex=sqrt((V(var2)$var2_power_centrality_stats+0.001)^2)/5,
     vertex.label.dist=0,
     rescale=F,
     xlim=range(co[,1]), 
     ylim=range(co[,2]))
axis(1)
axis(2)

#Solving Problems with legend rendering 
a<-V(var2)$var2_power_centrality_stats_r
b<-V(var2)$color_spower
c<-table(a,b)
d<-as.data.frame(c)
e<-subset(d, d$Freq>0)
f<-t(e$a)
g<-t(e$b)

#Adding Legend
legend(x=range(co[,1])[2], y=range(co[,2])[2],
       legend=as.character(f),
       pch=21,
       col = "#777777", 
       pt.bg=as.character(g),
       pt.cex=2,
       bty="n", 
       ncol=1,
       lty=1,
       cex = .5)

#Adding Title
  title("Bonacich Power Centrality Scores of Network Positions - Positive Attenuation - 4_REFERENCIA DE RECEBIMENTO CONTRAREFERENCIA (var2)", sub = "Source: from authors ")
  text(x=range(co[,1])[1], y=range(co[,2])[1], labels = 
   sprintf("Median Power Degree:%.2f\nSD Power Degree:%.2f",
     median(var2_power_centrality_stats),sd(var2_power_centrality_stats)
   ))
```


#Power (beta) Centrality Stats - (negative attenuation factor).

##Or are you more powerful if you're connected to weak, dependent people?

```{r, results="asis"}
#Saving power as an object
var2_power_centrality_stats_n <- power_centrality(var2, nodes = V(var2), loops = FALSE, exponent = -0.5, rescale = FALSE, tol = 1e-07, sparse = TRUE)

#Saving power as an igraph attributte
V(var2)$var2_power_centrality_stats_n <-power_centrality(var2, nodes = V(var2), loops = FALSE, exponent = -0.5, rescale = FALSE, tol = 1e-07, sparse = TRUE) 
```

##Power (beta) Centrality Stats - (negative attenuation factor).
```{r, results="asis"}
d=as.data.frame(cbind(V(var2)$LABEL_COR,round(var2_power_centrality_stats_n,2)))
names(d)<-c("Type", "Power(beta)")
datatable(d, filter ="top")
```

###Plotting Power Centrality Degree - (negative attenuation factor).
```{r, echo=FALSE, fig.height=12, fig.width=12, message=FALSE, warning=FALSE}

V(var2)$var2_power_centrality_stats_n <-try(power_centrality(var2, nodes = V(var2), loops = FALSE, exponent = -0.5, rescale = FALSE, tol = 1e-07, sparse = TRUE))

#Setting color for each vertex based on Power
V(var2)$var2_power_centrality_stats_r_n<-round(V(var2)$var2_power_centrality_stats_n,0)

# Creating brewer pallette
vertex_col_spower <- colorRampPalette(brewer.pal(length(unique(V(var2)$var2_power_centrality_stats_r_n)), "YlOrRd"))(length(unique(V(var2)$var2_power_centrality_stats_r_n))) 

#Saving as Vertex properties                             
V(var2)$color_spower <- vertex_col_spower[factor(V(var2)$var2_power_centrality_stats_r_n)]  

#Set Seed
set.seed(123)

#Plotting based only on degree measures 
edge.start <- ends(var2, es=E(var2), names=F)[,1]

# Fixing ego
minC <- rep(-Inf, vcount(var2))
maxC <- rep(Inf, vcount(var2))
minC[1] <- maxC[1] <- 0
co <- layout_with_fr(var2, niter=10000, minx=minC, maxx=maxC,miny=minC, maxy=maxC, weights = E(var2)$weight)

#PLotting
plot(var2, 
     layout=co,
     edge.color=V(var2)$color_spower[edge.start],
     edge.arrow.size=sqrt((V(var2)$var2_power_centrality_stats_r_n+0.001)^2)/10,
     edge.width=E(var2)$weight/(10*mean(E(var2)$weight)),
     edge.curved = TRUE,
     vertex.color=V(var2)$color_spower, 
     vertex.size=sqrt(((V(var2)$var2_power_centrality_stats_r_n+0.001)^2))*15,
     vertex.frame.color="#ffffff",
     vertex.label.color="black",
     vertex.label=V(var2)$V5_LABEL_LABEL,
     vertex.label.cex=sqrt((V(var2)$var2_power_centrality_stats_r_n+0.001)^2)/5,
     vertex.label.dist=0,
     rescale=F,
     xlim=range(co[,1]), 
     ylim=range(co[,2]))
axis(1)
axis(2)

#Solving Problems with legend rendering 
a<-V(var2)$var2_power_centrality_stats_r_n
b<-V(var2)$color_spower
c<-table(a,b)
d<-as.data.frame(c)
e<-subset(d, d$Freq>0)
f<-t(e$a)
g<-t(e$b)

#Adding Legend
legend(x=range(co[,1])[2], y=range(co[,2])[2],
       legend=as.character(f),
       pch=21,
       col = "#777777", 
       pt.bg=as.character(g),
       pt.cex=2,
       bty="n", 
       ncol=1,
       lty=1,
       cex = .5)

#Adding Title
  title("Bonacich Power Centrality Scores of Network Positions - Negative Attenuation - 4_REFERENCIA DE RECEBIMENTO CONTRAREFERENCIA (var2)", sub = "Source: from authors ")
  text(x=range(co[,1])[1], y=range(co[,2])[1], labels = 
   sprintf("Median Power Degree:%.2f\nSD Power Degree:%.2f",
     median(var2_power_centrality_stats_n),sd(var2_power_centrality_stats_n)
   ))
```


#Alpha Bonacich's centrality scores of network positions - positive attenuation factor

##Are you more powerful if you're connected to powerful people?

```{r, results="asis"}
#Saving power as an object
var2_alpha_centrality_stats <- try(alpha_centrality(var2, loops = FALSE, alpha = 0.5, exo = 1, weights=E(var2)$weight, tol = 1e-07, sparse = TRUE))

#Saving power as an igraph attributte
V(var2)$var2_alpha_centrality_stats<-try(alpha_centrality(var2, loops = FALSE, alpha = 0.5, exo = 1, weights=E(var2)$weight, tol = 1e-07, sparse = TRUE))

#Descriptive 
summary(var2_alpha_centrality_stats)
sd(var2_alpha_centrality_stats)
```

##Alpha Bonacich's Table - positive attenuation factor
```{r, echo=FALSE, fig.height=12, fig.width=12, message=FALSE, warning=FALSE}
d=as.data.frame(cbind(V(var2)$LABEL_COR, round(var2_alpha_centrality_stats,2)))
names(d)<-c("Type", "Alpha Bonacich")
datatable(d, filter ="top")
```

##Plotting Alpha Centrality Degree - positive attenuation factor
```{r, echo=FALSE, fig.height=12, fig.width=12, message=FALSE, warning=FALSE}
# Set colors to plot distances:
V(var2)$var2_alpha_centrality_stats_r<-round(V(var2)$var2_alpha_centrality_stats,0)

# Creating brewer pallette
vertex_col_s <- colorRampPalette(brewer.pal(length(unique(V(var2)$var2_alpha_centrality_stats_r)), "YlOrRd"))(length(unique(V(var2)$var2_alpha_centrality_stats_r))) 

#Saving as Vertex properties                                                                  
V(var2)$color_s <- vertex_col_s[factor(V(var2)$var2_alpha_centrality_stats_r)]  

#Set Seed
set.seed(123)

#Plotting based only on degree measures 
edge.start <- ends(var2, es=E(var2), names=F)[,1]

# Fixing ego
minC <- rep(-Inf, vcount(var2))
maxC <- rep(Inf, vcount(var2))
minC[1] <- maxC[1] <- 0
co <- layout_with_fr(var2, niter=10000, minx=minC, maxx=maxC,miny=minC, maxy=maxC, weights = E(var2)$weight)

#PLotting
plot(var2, 
     layout=co,
     edge.color=V(var2)$color_s[edge.start],
     edge.arrow.size=sqrt((V(var2)$var2_alpha_centrality_stats_r+0.0001)^2)/50,
     edge.width=E(var2)$weight/(10*mean(E(var2)$weight)),
     edge.curved = TRUE,
     vertex.color=V(var2)$color_s, 
     vertex.size=sqrt(((V(var2)$var2_alpha_centrality_stats_r+0.0001)^2))*2,
     vertex.frame.color="#ffffff",
     vertex.label.color="black",
     vertex.label=V(var2)$V5_LABEL_LABEL,
     vertex.label.cex=sqrt((V(var2)$var2_alpha_centrality_stats_r+0.0001)^2)/50,
     vertex.label.dist=0,
     rescale=F,
     xlim=range(co[,1]), 
     ylim=range(co[,2]))
axis(1)
axis(2)


#Solving Problems with legend rendering 
a<-V(var2)$var2_alpha_centrality_stats_r
b<-V(var2)$color_s
c<-table(a,b)
d<-as.data.frame(c)
e<-subset(d, d$Freq>0)
f<-t(e$a)
g<-t(e$b)

#Adding Legend
legend(x=range(co[,1])[2], y=range(co[,2])[2],
       legend=as.character(f),
       pch=21,
       col = "#777777", 
       pt.bg=as.character(g),
       pt.cex=2,
       bty="n", 
       ncol=1,
       lty=1,
       cex = .5)

#Adding Title
  title("Bonacich's Alpha Centrality Scores of Network Positions - Positive Attenuation - 4_REFERENCIA DE RECEBIMENTO CONTRAREFERENCIA (var2)", sub = "Source: from authors ")
  text(x=range(co[,1])[1], y=range(co[,2])[1], labels = 
   sprintf("Median Alpha Degree: %.2f\n SD Alpha Degree:%.2f",
     median(var2_alpha_centrality_stats),sd(var2_alpha_centrality_stats)
   ))
```

#Alpha Bonacich's centrality scores of network positions - negative attenuation factor

##Or are you more powerful if you're connected to weak, dependent people?

```{r, results="asis"}
#Saving power as an object
var2_alpha_centrality_stats_n <- try(alpha_centrality(var2, loops = FALSE, alpha = -0.5, exo = 1, weights=E(var2)$weight, tol = 1e-07, sparse = TRUE))

#Saving power as an igraph attributte
V(var2)$var2_alpha_centrality_stats_n<-try(alpha_centrality(var2, loops = FALSE, alpha = -0.5, exo = 1, weights=E(var2)$weight, tol = 1e-07, sparse = TRUE))

#Descriptive 
summary(var2_alpha_centrality_stats_n)
sd(var2_alpha_centrality_stats_n)
```

##Alpha Bonacich's Table - negative attenuation factor
```{r, echo=FALSE, fig.height=12, fig.width=12, message=FALSE, warning=FALSE}
d=as.data.frame(cbind(V(var2)$LABEL_COR, round(var2_alpha_centrality_stats_n,2)))
names(d)<-c("Type", "Alpha Bonacich")
datatable(d, filter ="top")
```

##Plotting Alpha Centrality Degree - negative attenuation factor
```{r, echo=FALSE, fig.height=12, fig.width=12, message=FALSE, warning=FALSE}
# Set colors to plot distances:
V(var2)$var2_alpha_centrality_stats_r_n<-round(V(var2)$var2_alpha_centrality_stats_n,0)

# Creating brewer pallette
vertex_col_s <- colorRampPalette(brewer.pal(length(unique(V(var2)$var2_alpha_centrality_stats_r_n)), "Blues"))(length(unique(V(var2)$var2_alpha_centrality_stats_r_n))) 

#Saving as Vertex properties                                                                  
V(var2)$color_s <- vertex_col_s[factor(V(var2)$var2_alpha_centrality_stats_r_n)]  

#Set Seed
set.seed(123)

#Plotting based only on degree measures 
edge.start <- ends(var2, es=E(var2), names=F)[,1]

# Fixing ego
minC <- rep(-Inf, vcount(var2))
maxC <- rep(Inf, vcount(var2))
minC[1] <- maxC[1] <- 0
co <- layout_with_fr(var2, niter=10000, minx=minC, maxx=maxC,miny=minC, maxy=maxC, weights = E(var2)$weight)

#PLotting
plot(var2, 
     layout=co,
     edge.color=V(var2)$color_s[edge.start],
     edge.arrow.size=sqrt((V(var2)$var2_alpha_centrality_stats_r_n+0.0001)^2)/10,
     edge.width=E(var2)$weight/(10*mean(E(var2)$weight)),
     edge.curved = TRUE,
     vertex.color=V(var2)$color_s, 
     vertex.size=sqrt(((V(var2)$var2_alpha_centrality_stats_r_n+0.0001)^2))*5,
     vertex.frame.color="#ffffff",
     vertex.label.color="black",
     vertex.label=V(var2)$V5_LABEL_LABEL,
     vertex.label.cex=sqrt((V(var2)$var2_alpha_centrality_stats_r_n+0.0001)^2)/25,
     vertex.label.dist=0,
     rescale=F,
     xlim=range(co[,1]), 
     ylim=range(co[,2]))
axis(1)
axis(2)


#Solving Problems with legend rendering 
a<-V(var2)$var2_alpha_centrality_stats_r_n
b<-V(var2)$color_s
c<-table(a,b)
d<-as.data.frame(c)
e<-subset(d, d$Freq>0)
f<-t(e$a)
g<-t(e$b)

#Adding Legend
legend(x=range(co[,1])[2], y=range(co[,2])[2],
       legend=as.character(f),
       pch=21,
       col = "#777777", 
       pt.bg=as.character(g),
       pt.cex=2,
       bty="n", 
       ncol=1,
       lty=1,
       cex = .5)

#Adding Title
  title("Bonacich's Alpha Centrality Scores of Network Positions - Negative Attenuation - 4_REFERENCIA DE RECEBIMENTO CONTRAREFERENCIA (var2)", sub = "Source: from authors ")
  text(x=range(co[,1])[1], y=range(co[,2])[1], labels = 
   sprintf("Median Alpha Degree: %.2f\n SD Alpha Degree:%.2f",
     median(var2_alpha_centrality_stats_n),sd(var2_alpha_centrality_stats_n)
   ))
```


#Saving objects with new variables and changes
```{r, echo=T, fig.height=12, fig.width=12, message=FALSE, warning=FALSE}
save.image("~/SNArRDJF/Robject/6_bonacichs_var2.RData") 
```

