---
title: "SNA Edge Betwenness 7_OFERTA DE TREINAMENTOS CAPACITAÇÕES (var5)"
author: "Leonardo Martins"
date: "17 de julho de 2016"
output: 
  html_document: 
    fig_caption: yes
    fig_height: 12
    fig_width: 12
    keep_md: yes
    number_sections: yes
    theme: flatly
    toc: yes
---
SNA Descritive Analysis from "Projeto Redes de Atenção às pessoas que consomem álcool e outras Drogas em Juiz de Fora-MG   Brazil"  - SNArRDJF

Here you can find a basic script to analysis data from SNArRDJF - this script was elaborated considering its use for orther matrix adjacency data from SNArRDJF - Here we are going to analyse:

# 7_OFERTA DE TREINAMENTOS CAPACITAÇÕES (var5)

`#########################
`# Basic Preparation #####
`#########################

#Loading objects generated with previous script 
```{r, echo=TRUE, fig.height=12, fig.width=12, message=FALSE, warning=FALSE}
rm(list = ls()) # removing previous objects to be sure that we don't have objects conflicts name
load("~/SNArRDJF/Robject/10_distance_paths_var5.RData")
```
##Reload packages
```{r, message=TRUE, warning=TRUE}
suppressMessages(library(RColorBrewer))
suppressMessages(library(car))
suppressMessages(library(xtable))
suppressMessages(library(igraph))
suppressMessages(library(miniCRAN))
suppressMessages(library(magrittr))
suppressMessages(library(keyplayer))
suppressMessages(library(dplyr))
suppressMessages(library(feather))
suppressMessages(library(visNetwork))
suppressMessages(library(knitr))
suppressMessages(library(DT))
```
##Adding phantom tools
```{r, message=TRUE, warning=TRUE}
#In order to get dinamic javascript object install those ones. If you get problems installing go to Stackoverflow.com and type your error to discover what to do. In some cases the libraries need to be intalled in outside R libs.
#devtools::install_github("wch/webshot")
#webshot::install_phantomjs()
```
##Setting a random seed - this is a good strategy to keep the same graph pattern layout in a new report generation
```{r, message=TRUE, warning=TRUE}
set.seed(123)
```

##Simplify Graph - removing loops and duble edges 
```{r, echo=T, message=FALSE, warning=FALSE}
#var5<-simplify(var5) #Simplify
```

#Edges Newman-Girvan Edge-Betweenness - Non-Weighted
Edge betweenness Edge betweenness is equal to the number of shortest paths σst(e) from all vertices to all others that pass through that edge e
```{r, echo=TRUE, fig.height=12, fig.width=12, message=FALSE, warning=FALSE}
#Edge Betweenness
E(var5)$edge.betweenness_n<-edge.betweenness(var5, weights =E(var5)$equalone)
var5_edge.betweenness_n <-edge.betweenness(var5, weights =E(var5)$equalone)
```
#Edge Betweenness Descriptive
```{r, echo=TRUE, fig.height=12, fig.width=12, message=FALSE, warning=FALSE}
summary(var5_edge.betweenness_n)
sd(var5_edge.betweenness_n)
```

#Edges Newman-Girvan Edge-Betweenness - Weighted
Edge betweenness Edge betweenness is equal to the number of shortest paths σst(e) from all vertices to all others that pass through that edge e
```{r, echo=TRUE, fig.height=12, fig.width=12, message=FALSE, warning=FALSE}
#Edge Betweenness
E(var5)$edge.betweenness<-edge.betweenness(var5, weights =E(var5)$var5)
var5_edge.betweenness <-edge.betweenness(var5, weights =E(var5)$var5)
```
#Edge Betweenness Descriptive
```{r, echo=TRUE, fig.height=12, fig.width=12, message=FALSE, warning=FALSE}
summary(var5_edge.betweenness)
sd(var5_edge.betweenness)
```

#Betweenness Edge Dinamic Table
```{r, echo=TRUE, fig.height=12, fig.width=12, message=FALSE, warning=FALSE}
#Betweenness Measures Dinamic Table
#Getting  Measures
var5_edge.betweenness_n <-edge.betweenness(var5, weights =E(var5)$equalone)
var5_edge.betweenness <-edge.betweenness(var5, weights =E(var5)$var5)

#Creating a dataframe of measures
var5_df_betweenness <- data.frame(var5_edge.betweenness_n ,
var5_edge.betweenness) %>% round(1)

labels<-attr(E(var5), "vnames")
#edgebt<-cbind(round(var5_edge.betweenness,2),labels)

#Adding type
var5_df_betweenness <-cbind(var5_df_betweenness, labels)

#Adding names
names(var5_df_betweenness) <- c("Edge Betweenness", "Edge Betweenness Weighted", "Type")

#Ordering Variables
var5_df_betweenness<-var5_df_betweenness[c("Type","Edge Betweenness", "Edge Betweenness Weighted")]
```
## General tabel for Betweenness
```{r, echo=TRUE, fig.height=12, fig.width=12, message=FALSE, warning=FALSE}
datatable(var5_df_betweenness, filter = 'top')
```
##Aggregating data from previous table - mean
```{r, echo=TRUE, fig.height=12, fig.width=12, message=FALSE, warning=FALSE}
aggdata_mean <-aggregate(var5_df_betweenness, by=list(var5_df_betweenness$Type), FUN=mean, na.rm=TRUE)

names(aggdata_mean) <- c("Group","Type","Betweenness(M)", "Betweenness Weighted(M)")
  
#Removing Type variable
aggdata_mean<-aggdata_mean[,-c(2)]
```
##Aggregating data from previous table - sd
```{r, echo=TRUE, fig.height=12, fig.width=12, message=FALSE, warning=FALSE}
aggdata_sd <-aggregate(var5_df_betweenness, by=list(var5_df_betweenness$Type), FUN=sd, na.rm=TRUE) 

names(aggdata_sd) <- c("Group","Type","Betweenness(SD)", "Betweenness Weighted(SD)")

#Removing Type variable
aggdata_sd<-aggdata_sd[,-c(2)]
```
##Merging mean and standart deviation
```{r, echo=TRUE, fig.height=12, fig.width=12, message=FALSE, warning=FALSE}
total_table<- merge(aggdata_mean,aggdata_sd,by="Group")

#Rounding
Group<-total_table[,c(1)] #Keeping group
total_table<-total_table[,-c(1)] %>% round(1) #Rouding
total_table<-cbind(Group,total_table) #Binding toghter

#Organizing Variabels
total_table<-total_table[c("Group","Betweenness(M)","Betweenness(SD)","Betweenness Weighted(M)", "Betweenness Weighted(SD)")]
```
##Plotting final table with round
```{r, echo=TRUE, fig.height=12, fig.width=12, message=FALSE, warning=FALSE}
datatable(total_table, filter = 'top')
```

#Network plotting based only on degree measures 
```{r, echo=TRUE, fig.height=12, fig.width=12, message=FALSE, warning=FALSE}
#Set Seed
set.seed(123)
#Plotting based only on degree measures 
edge.start <- ends(var5, es=E(var5), names=F)[,1]

# Fixing ego
minC <- rep(-Inf, vcount(var5))
maxC <- rep(Inf, vcount(var5))
minC[1] <- maxC[1] <- 0
co <- layout_with_fr(var5, niter=10000, minx=minC, maxx=maxC,miny=minC, maxy=maxC, weights =E(var5)$edge.betweenness)

min(E(var5)$edge.betweenness)
#PLotting
plot(var5, 
     layout=co,
     edge.color=V(var5)$color[edge.start],
     edge.arrow.size=E(var5)$edge.betweenness/10000*mean(E(var5)$edge.betweenness+1),
     edge.width=E(var5)$var5/10*mean((E(var5)$var5+1)),
     edge.curved = TRUE,
     vertex.size=log((degree(var5)+2))*(0.5*mean(degree(var5))),
     vertex.frame.color="#ffffff",
     vertex.label.color="black",
     vertex.label=get.vertex.attribute(var5,"LABEL_COR"),
     vertex.label.cex=log(degree(var5)+2)/mean(degree(var5)),
     vertex.label.dist=0,
     rescale=F,
     xlim=range(co[,1]), 
     ylim=range(co[,2]))
axis(1)
axis(2)


#Solving Problems with legend rendering 
a<-V(var5)$LABEL_COR
b<-V(var5)$color
c<-table(a,b)
d<-as.data.frame(c)
e<-subset(d, d$Freq>0)
f<-t(e$a)
g<-t(e$b)

#Adding Legend
legend(x=range(co[,1])[2], y=range(co[,2])[2],
       legend=as.character(f),
       pch=21,
       col = "#777777", 
       pt.bg=as.character(g),
       pt.cex=2,
       bty="n", 
       ncol=1,
       lty=1,
       cex = .5)

#Adding Title
  title("Network Edge Betweenness Sized - 7_OFERTA DE TREINAMENTOS CAPACITAÇÕES (var5)", sub = "Source: from authors ", cex = .5)
  text(x=range(co[,1])[1], y=range(co[,2])[1], labels = 
   sprintf("Mean Betweenness : %.2f\n SD Betweenness : %.2f",
     mean(E(var5)$edge.betweenness), 
     sd(E(var5)$edge.betweenness)
   ))
```


#Saving objects with new variables and changes
```{r, echo=T, fig.height=12, fig.width=12, message=FALSE, warning=FALSE}
save.image("~/SNArRDJF/Robject/11_ebetweenness_var5.RData") 
```

